Kelp morphometric properties and the link to hydrodynamic modelling

### 2018-09-21 proposal_draft_2018.Rmd
more additions and edits to the wave exposure section
some minor edits and additions to the hydrodynamic model section

The hydrodynamic model for coastal flow will be developed using already existing models that have been developed. These models will consist of the SWAN and Delf3D models and the apporach is to use aspects of each model, that are related to coastal flow, from which further development will take place. Once the model has been developed it will be used to predict kelp morphology at random sites which will then be sampled. The *in situ* kelp morphology data collected at the predicted site will be used to calibrate the model. This process will be repeated until the model can predict coastal flow and kelp morphology within a certian degree of probability.

@@

Months | Description
------------------------------ | -------------------------------------------
April 2018 - September 2018 | Develop and write proposal for submission to department
September 2018 - December 2018 | Acceptable level of progress on literature review. The first data chapter should also be complete and submission of first paper
January 2019 - May 2019 | Become competent in relevant software (Python). Data analyses for the 2nd data chapter should ideally be near completion. Substantial additions to literature review. 
May 2019 - August 2019| Completion of 2nd data chapter and relevant paper should also be near completion. 
August 2019 - December 2019 | Complete analyses and write-up for final data chapter. Significant progress on the relevant paper. Literature review should be near completion. 
January 2020 - April 2020 | This time will be used to make final edits and complete thesis write-up

>>>>

The hydrodynamic model for coastal flow will be developed using already existing models that have been developed. These models will consist of the SWAN and Delf3D models and the apporach is to use aspects of each model, that are related to coastal flow, from which further development will take place. Once the model has been developed it will be used to predict kelp morphology at random sites which will then be sampled. The *in situ* kelp morphology data collected at the predicted site will be used to calibrate the model. This process will be repeated until the model can predict coastal flow and kelp morphology within a certian degree of probability. Kelp morphology is driven by regional and local environmental factors, the spatial scales used will be dependent on the spatial patterns of the various abiotic variables being investigated. Fully nested hierarchical design at three spatial scales will be used: regions, locations (within regions) and sites (within locations).

@@

Months | Description
------------------------------ | -------------------------------------------
April 2018 - September 2018 | Develop and write proposal for submission to department
September 2018 - December 2018 | Acceptable level of progress on literature review. The first data chapter should also be complete and submission of first paper
January 2019 - May 2019 | Become competent in relevant software (Python). Data analyses for the 2nd data chapter should ideally be near completion. Substantial additions to literature review. 
May 2019 - August 2019| Completion of 2nd data chapter and relevant paper should also be near completion. 
August 2019 - December 2019 | Complete analyses and write-up for final data chapter. Significant progress on the relevant paper. Literature review should be near completion. 
January 2020 - June 2020 | Complete of final data chapter and final chapter.
June 2020 - December 2020 | This time will be used to make final edits and complete thesis write-up
